|

### 2025-01-21 paper/submission2/response.md

--- 
title: "Response to editor and reviewer comments"
bibliography: bibliography.bib
output: html_document
---

@@

Thank you for submitting your manuscript to Journal of Economic Geography.

I have now received comments from reviewers. Their comments are at the end of this email. The reviewers raise a range of concerns and have questions about the suitability of the paper for publication. The overall feeling is that the paper has probably been submitted too early and needs major work on most sections if it is to become publishable. I concur with the reviewers and see a number of significant issues that need to be addressed. This left me with a dilemma in terms of the decision. I have decided to invite you to revise and resubmit the paper so that it can be considered further for publication. However, this is a very high-risk revision, and I was bordering on rejection given the scale of the work needed and the limitations that the reviewers highlight. I am saying this to be open about the risk that after the next round the paper could be rejected unless reviewers believe you have addressed the range of issues identified. You may want to factor this into your decision about whether to revise the paper, given how much work is needed.

Having said this, let me offer some suggestions about the main areas to focus on if you decide to revise the paper. Reviewer 1 is more positive but very brief in their report. I am, therefore, putting more weight on reviewers 2 and 3 when identifying priorities for the revision.

## Editor; theory and justification 
First, you will need to develop a more convincing theoretical argument and contribution. You will see that both reviewers 2 and 3 raise questions about your claims in relation to the gap in the literature and suggest you fail to build on existing work appropriately and do not convincingly identify the motivation for this analysis. In general, claims that an issue has never been addressed are hard to sustain and it is better to build on existing work and extend knowledge relating to a particular theoretical issue. The reviewers challenge you to do this using your data and suggest both the argument and structure of the paper will need to change.

## Editor; data
Second, you need to justify your data and analysis better. Reviewer 2 fairly questions the end point of the analysis – which is not explained and given the 10+ years gap to your submission raises questions about the timeliness of the analysis. The questions about coverage of the UK website population also need to be addressed convincingly. More generally, the reviewers ask for more careful presentation of the data to make clear the significance of each figure and finding. As it stands, the paper feels rather overloaded with data, rather than acting as a focused analysis.

## Editor; conclusions
The problems identified above result in the paper feeling imprecise, confusing and lacking a contribution. The end point is a conclusion that the reviewers do not find justified or original. The reviewers do see potential. As I noted, the feeling is a paper that is underdeveloped and submitted prematurely. There is, then, a route to publication, but it will require significant changes to convince the reviewers.

@@

> Simplify the Introduction: I recommend streamlining the introduction by reducing the inclusion of overly technical or highly specific details. Instead, consider expanding on the broader conceptual framework that situates the paper within its scholarly context. This approach would help orient readers and provide a more accessible foundation for understanding the study.
*Simplify the introduction*

Strengthen the Connection Between Hypotheses and Results: It may be beneficial to establish a clearer and more explicit link between the study's hypotheses and its findings. One way to achieve this could be by using section titles that are more conceptually informative, which would guide the reader through the logical progression of the argument and findings more effectively.
*change section titles?*

## Referee: 2

Comments to the Author
OVERVIEW
- focused on innovation diffusion, using the case of the web in the UK
- “this paper tests whether the three distinct spatial diffusion mechanisms shaped the diffusion of the Web in the UK at very granular spatial scales from the Web’s early stages onwards”; presumably “S-shaped pattern”/temporal models, core to periphery; distance/proximity.

> Figure 2 shows the diffusion of domains per company at the scale of the UK matches the S growth model. Figure 3 shows some spatial clustering. I think this is for all years in the dataset but this could be better labeled
*explain, change title*

> Figure 4, not sure what this demonstrates

> Figure 5&6, shows early clustering and then diffusion (I think)
*yes*

DATA
> Focusing just on .co.uk website is OK but needs to be better justified given that it only represented about 50 percent of domains in the UK at that time. See my back of the envelop calculations: As per Zook (2001, Table 1) .uk represented 66% of all domains in the UK, .co.uk is a subset of that, so this is perhaps 50% of all domains registered in the UK at that time. If 1/5 of .co.uk domains had findable postal codes (p. 5), this study is based on 10% of the domains in the UK. (perhaps this is too low, aggregating from webpages to websites brought the number higher, not entirely clear to me)

Thanks for going the extra mile to check the data used here! I agree with the 
above calculation up until the findable postcode point as 1/5 of the archived 
*webpages* -- not *websites*, i.e. domains -- included a postcode in the web text. 
Think of the website of a small company with one trading address. I think it is 
fair to expect that website to have multiple webpages to present the different
products and services and then one webpage to showcase the address -- the 
'Contact us' page. So, the 1/5 share of *webpages* containing a postcode should
translate to a much higher share of *websites* -- i.e. domains -- containing 
a postcode. Previous estimates indicated that around 70% of all websites contain 
place reference [@hill2009georeferencing] and this reference has no been added 
in the paper. **ADD REF**

@@

So, based on the above 35% of all domains with a registered address in the UK
were represented in the data. Most importantly though the paper does not model the 
adoption of the Web from the general population but instead from firms. So, 
although the data only represents 35% of the population of websites with a 
registered address in the UK, it represents almost all the *relevant* archived
websites -- that is websites using the commercial .co.uk SLD. As stated in the 
paper, this has been the primary choice for commercial websites in the UK.

Active/inactive, don;t suffer from multiple registrations

Third paragraph in the Data and Methods section. 
"Instead of using the whole .uk ccTLD, this paper focuses on its
commercial subset, the .co.uk second level domain (SLD). This choice
is aligned with the topic of the paper -- the diffusion of the Web for 
commercial functions and decreases the heterogeneity of the web data as such 
commercial websites have specific aims: they are used to diffuse information, 
support online transactions and share opinions [@THELWALL2000441; 
@blazquez2018big]".

**FIX TEXT TO EMPHASISE THE COMMERCIAL - LINK TO R3**

*rebutal: this is not about general population web adoption, but firms, which more often than not use .co.uk*

> - overall the time period 1996-2012 is a good time to study the diffusion of the commercial internet. But why stop at 2012? Is it when the Library stopped its data series?
*yes, explain the internet archive data. But also say that this is okay given that after 2012 the curve was flattened*

Framing
>“With the exception of Sinai and Waldfogel (2004), who focused, among other things, on web content and demonstrated that more such content is available in larger markets, this strand of literature has been mostly concerned with the spatiality of the Internet’s hard and tangible infrastructure and shied away from exploring the spatial dimensions of one of the most distinct software layers of the Internet infrastructure, the Web.” This statement is simply not true, the literature reviews misses the entirety of web content diffusion studies: Zook, 2000, Malecki, 2002. Townsend, 2000, Gorman, 2002, Feldman, 2002, lots more

Para has been changed and added a long time series motivation. @zook2000web, @zook2000web and 
@moss1997tracking used domain name registration data, but rest (e.g. @malecki2002economic and @moss2000internet) used focused on hard infrastructure.

>“for a digital technology as weightless as the Web” – this runs a bit counter to lots of work by digital geographers who have shown again and again how the digital is not weightless or placeless

Conclusion
>p. 18 “This is the first time that the importance of granular spatial mechanisms for the diffusion of an intangible, digital technology is exposed.” Honestly, I would not expect the diffusion of the web to be any different than any other kind of innovation diffusion. The spatiality of digital life, and its connection to material spaces is a constant refrain within digital geography. So I’m not convinced it makes much sense to emphasize this, if a granular spatial analysis of innovation diffusion is already novel.

*for the last two comments, I need to soften the weightless argument throughout.* 
I have added a long time series argument and also said that there is heterogeneity
[@leibowicz2016representing] among diffusion rates of different technologies.

The digital motivation para in the introduction has been ammended accordilngly.

@@

## Referee: 3

Comments to the Author
Review JOEG-2024-369: A multi-scale story of the diffusion of a new technology: the web

This paper addresses a gap in Economic Geography by examining the spatial diffusion of digital technologies, specifically the adoption of commercial websites, from 1996 to 2012. Recognizing the potential of digital technologies to shape local development trajectories through increased productivity and innovation, the study employs novel data sources and machine learning techniques to analyze diffusion patterns at highly granular geographical scales. The authors explore the roles of various spatial mechanisms driving this process, offering insights into how digital technology adoption unfolds across space and time.
The paper has the potential to make an interesting contribution to the literature as it combines a fascinating topic with novel data and methodologies. However, in its current form, it is not ready for publication, as it never becomes clear what it actually delivers in terms of new knowledge and what knowledge gap it seeks to fill. Despite some analytical elements, it is rather descriptive in nature, which doesn’t fit well with this journal.

> Most importantly, I suggest developing some clear hypotheses to structure and motivate the paper better. In light of this, I recommend major revisions.

Hypotheses have been added.

>1. Abstract:
1. The abstract needs significant improvement. It needs to adequately report the main findings, relevance, or implications of the study. Additionally, the assertion that geographers have "shied away" from analyzing the diffusion of digital technologies is misleading; the issue was primarily due to the lack of available data.

2. Introduction
>2. General Diffusion Studies: The statement that there are few contemporary general diffusion studies in Economic Geography is not accurate, although it may apply specifically to digital technologies. Consider the following recent examples:
o Peris, A., Meijers, E., & van Ham, M. (2021). Information diffusion between Dutch cities: Revisiting Zipf and Pred using a computational social science approach. Computers, Environment and Urban Systems, 85(November), 101565. https://doi.org/10.1016/j.compenvurbsys.2020.101565
o Bednarz, M., & Broekel, T. (2020). Pulled or pushed? The spatial diffusion of wind energy between local demand and supply. Industrial and Corporate Change, 29(4), 893–916. https://doi.org/10.1093/icc/dtaa012
o Feldman, M. P., Kogler, D. F., & Rigby, D. L. (2015). rKnowledge: The Spatial Diffusion and Adoption of rDNA Methods. Regional Studies, 49(5), 798–817. https://doi.org/10.1080/00343404.2014.980799

Peris et al. (2021) is not directly relevant as it focuses on information 
diffusion rather than diffusion of innovations or new technologies.  Bednarz et 
al (2020) was already cited in the first submission. Feldman et al (2015) has 
now been cited. These references are included in the literature section.

Regarding the statement about economic geography studies on diffusion of 
new technologies and innovation, I do believe that this is a fair statement. 
The references listed below are the ones reviewed in the second section and none of 
them are published in one of the flagship economic geography journals 
(*Journal of Economic Geography* and *Economic Geography*). There two papers
published in *The Professional Geographer*, which is a broad-scope geography 
journal and then only one paper in *Regional Studies*, which is the closest to
economic geography. Importantly though, the *Regional Studies* paper 
[@feldman2015rknowledge] paper is focused on inventions as observed by patent 
data contrary to the broader 'adoption of a new technology' approach of this paper.
All other papers listed below are published in business and economics journals.

@@

1. @beardsell1999spatial: European Economic Review
2. @bednarz2020pulled: Industrial and Corporate Change
3. @haller2011determinants: Applied Economics
4. @perkins2011internet: The Professional Geographer
5. @feldman2015rknowledge: Regional Studies
6. @ding2010modeling: The Professional Geographer
7. @bakher2013diffusion: Journal of Marketing Analytics
8. @PAPAGIANNIDIS2015308: Technological Forecasting and Social Change
9. @lengyel2020role: Scientific reports

Also, the lack of spatial granularity argument has been highlighted in various 
instances throughout the paper:

*ADD SPATIAL GRANULARITY IN CONCLUSIONS*
Added in intro and lit rev. Made it key justification as highlighted by Reviewer 1.

> 3. Novelty: The study needs to be more explicit about its novel contributions to understanding spatial diffusion mechanisms. Currently, the discussion is too general.

granularity

*HAVE A THINK*

>4. Motivation: The motivation for the study is unclear. The text raises several issues, but it is unclear which are specific to digital technologies and which pertain to technological diffusion more broadly.

*HAVE A THINK*

>5. Structure and Focus: The discussion on motivations should be streamlined and clarified. For example, after specifying that the study focuses on commercial websites rather than the web, subsequent references revert to the general term “web.” Additionally, the discussion confuses diffusion patterns, firm perspectives, and early adopter advantages. Consider restructuring this section to clearly differentiate between literature gaps (motivations) and expected outcomes (mechanisms).

**LINK WITH REVIEWER 2 ABOUT WEB DATA**

@@

The introduction and literature review sections have been restructured, so 
the firm perspectives and early adopter advantages discussions have been moved.

> 6. Data Consistency: The terminology for the data should be consistent. At one point, the text refers to the “totality of the web,” while elsewhere, it specifies “commercial websites.” Clarify and maintain consistency throughout.

The terminology is consistent across the paper now. The "totality" point referred 
to different web technologies. Now it has been replaced as "an overarching technology".

7. Recommended Structure: To align with the common structure in Journal of Economic Geography (JoEG), consider splitting the introduction into a shorter introduction and a dedicated theory section merged with the literature review.

3. Literature Review / Theory
> 1. Synthesis and Motivation: The literature review should be transformed into a theory section. Rather than presenting a historical review, synthesize the arguments to clearly motivate and inform your hypotheses.

@@

Known processes at very detailed scale: explanatory power of these mechanisms at granular, local
scales

> 3. Lack of Hypotheses: To clarify what the paper delivers and what knowledge gaps it fills, I strongly recommend developing a number of hypotheses that will be tested.

Added.

> 4. Fit to title: The term “multi-scalar” appears in the title but is never really discussed in the paper.

Added before H~2~.

4. Data & Methods
1. Order of Presentation: Introduce the data first, followed by the geographical units used in the study.
2. Postcode Identification: The approach of identifying postcodes on websites is innovative, but potential errors need to be discussed. Specifically:
>o How do you ensure that a postcode on a website accurately represents the company’s location or its subsidiary?
*trading address, one to many postcodes*

>o How do you handle numbers that resemble postcodes but are not actual postcodes?
*matched with postcode lookup file*

>o What about references to events or other organizations unrelated to the website’s owner?
*we cannot distinguish, but 1-10 postcodes*
Include a brief discussion of these potential issues.

>3. Equation 2: The rationale behind Equation 2 is unclear. Shouldn’t the primary predictor of website density at time tbe the location density at t-1? Why was this approach chosen over a growth model? Additionally, clarify how spatial dependencies are accounted for in the model.
*growth as an appendix, spatial dependencies have been included*

5. Results
>1. Diffusion Speed: The decision to binarize diffusion speed is questionable. Continuous measures, such as growth rates or the time required to reach 50% saturation, would provide more informative insights.
*This is only for the map, this is a critical point in diffusion studies*

> 2. Geographical Scale: While the effort to model diffusion curves at a fine geographical scale is commendable, the paper does not sufficiently explain the benefits or additional knowledge gained from this approach.

> 3. Early Adopters and Latecomers: The discussion of early-adopter and latecomer advantages is underdeveloped. How do these advantages manifest locally? What specific benefits arise if a company registers its website six months earlier than competitors in other locations? If this aspect is retained, it should be elaborated in the theory section, including how it relates to local capabilities or diffusion hierarchies.

4. Descriptive Statistics: The value of the descriptive Moran’s I and Gini coefficient analyses in Section 4.2 is unclear. Instead, calculating growth rates of adoption and examining their distribution over time would offer a better sense of adoption speed and magnitude.

5. Retail Centers: The sudden shift to retail centers on page 15 is confusing, given that the data pertains to all commercial sites. Clarify the rationale for this focus.

6. Modeling Details: The methodological details in Section 4.3 should be moved to the methods section to maintain clarity and coherence. Including these details in the results section is confusing.

7. Clarity and Structure: Section 4.3 is difficult to follow. Clearly state the main message and highlight how diffusion mechanisms vary spatially. Develop hypotheses to structure the results and provide potential explanations for observed heterogeneity. Without this, the section feels like a descriptive summary without clear takeaways for the reader.

Overall Recommendations
1. Consistency: Ensure consistent terminology and focus throughout the paper, particularly when referring to the web and commercial websites.
2. Structure: Adopt a clearer structure by separating the introduction, theory/literature review, methods, and results sections.
3. Clarity: Develop hypotheses to frame the results and provide clearer explanations for methodological choices and findings.

### 2025-01-21 Untitled/Untitled.Rmd

---
title: Title of submission to PLOS journal
author:
  - name: Emmanouil Tranos
    email: e.tranos@bristol.ac.uk
    affiliation: University of Bristol and The Alan Turing Institute
    corresponding: e.tranos@bristol.ac.uk
address:
  - code: University of Bristol and The Alan Turing Institute
    address: University of Bristol, School of Geographical Sciences, Bristol, UK; The Alan Turing Institute, London, UK
abstract: |
  blah blah

author_summary: |
  blah blah
bibliography: mybibfile.bib
output: rticles::plos_article
csl: plos.csl
header-includes:
- \usepackage{rotating, graphicx, dcolumn, booktabs, caption, xcolor}
editor_options: 
  markdown: 
    wrap: 72
---

```{r echo=FALSE, message = FALSE, warning=FALSE}
library(stargazer)
library(tidyverse)
#library(rmarkdown)
```

# Introduction {#sec:1}

@beardsell1999spatial To characterize evolution of the computer
industry, we examine the distribution of relative employment across
cities in 1977 and how that distribution changes over time to 1992

There is no tendency of relative size distributions of urban computer
employment to collapse, go bimodal, or fully spread. Overall computers
exhibit some turbulence, with dramatic big winners and losers among
cities. In attracting or repelling an industry, urban heterogeneity is
important. Large, well educated cities near San Jose have much greater
chances of attracting high-tech employment and less of losing it

@bednarz2020pulled spatial innovation diffusion By using Bayesian
survival models with time-dependent data of wind turbine deployment and
firm foundation for 402 German regions between the years 1970 and 2015,
we show that the spatial evolution of the German wind energy industry
was more strongly influenced by local demand-- pull than local
supply--push processes.

The industry's initial locations are distributed relatively arbitrarily
and unpredictably, as their needs in terms of resources and skills are
diverse and distinct from the older existing industries (Boschma and
Lambooy, 1999). Consequently, emerging industries are characterized by
relatively high degrees of freedom in terms of location. In later
extensions of the concept, the assumption of the randomness of locations
was revised with greater importance assigned to regional conditions
(Boschma and Lambooy, 1999; Fornahl et al., 2012).

larger local technological niches (at least from a demand perspective)
are more likely to be formed in urban areas than in rural ones, which is
in line with the work of Ha¨gerstrand (1965a,b). However, size is not
the only regional characteristic that may matter in this context.
Regions also differ in accumulated experiences and the presence of tacit
knowledge with respect to products, as well as in actors' propensity
share this knowledge among producers (Martin et al., 2019)

@bento2015spatial The concept of absorptive capacity has also been
applied in the TIS context in terms of the con-struction of capacity
needed to transfer and implement a new technology in the receiving
country (cf.Van Alphen, 2011), with repercussions for the nature of
system functions

@das2022diffusion [not good paper] Invention, innovation and diffusion
are considered as the three pillars of the theory of technological
change and Schumpeter is considered as the father of the study of
diffusion

Epidemic approach: The approach emphasizes that the adoption of a
technology spreads like an infection among the potential adopters. By
taking a homogeneous group of potential adopters as an assumption, it
explains the adoption of any innovation.

To summarize the discussion, first, here the diffusion process is
selfperpetuating as initial use stimulates further use. Second, it
follows a disequilibrium path as the level of users is always lower than
the number of potential users (Stoneman 2002).

The criticisms are mainly based on the fact that although the approach
gives an idea of aggregate (industry or household) behaviour, it does
not focus on the individual's (firm or household) adoption process

Rogers3, that divides adopters as: (I.) Innovators: first 2.5%, (II.)
Early adopters: next 13.5%, (III.) Early Majority: following 34%, (IV.)
Late Majority: next 34%, and the rest as (V.) Laggards

@morrill2020spatial Spatial diffusion is the process by which behavior
or characteristics of the landscape change as a result of what happens
elsewhere earlier. Spatial diffusion is the spread of the phenomenon,
over space and timed, from limited origins

Contagious diffusion=\> spatial autocorelation

expansion-type diffusion

the three geographic diffusion processes are (1) purely contagious where
distance or adjacency is the absolute controlling factor, (2) purely
hierarchical where size or urban position in the central place hierarchy
is the absolute controlling factor, or (3) where the location of change
is purely random. These are the pure or ideal forms of the diffusion
process; all real diffusion processes are the result of a combination of
these extremes.

The work by the communication sociologist Everett Rogers (1962, 1971,
1983) has emphasized the role of information, communication, formal and
informal media, opinion leaders and social networks, and economic and
psychological constraints on acceptance. Rogers's work stresses the
decision mechanism of the potential adopter; the work of Rogers
partitions the adopter's process of choosing to accept a new phenomenon
or trait into five stages: stage 1--the potential adopter gains
knowledge or awareness of an innovation; stage 2--persuasion is
exercised to adopt; stage 3--a decision is made to adopt; stage 4--the
decision to adopt is implemented; stage 5--the adopter confirms the
decision to adopt. In Rogers's stage theory there may be a substantial
time lag between when a potential adopter becomes aware of the new
characteristic and when a decision is actually made to adopt.

Hägerstrand considered diffusion to be a fundamental geographic process:
Whatever the phenomenon being diffused might be, one may consider it in
the context of a larger universal process of spatial diffusion.

@zook2022mapping Because new digital activities are rarely---if
ever---captured in official state data, researchers must rely on
information gathered from alternative sources. With this in mind, the
overarching aim of this article is outlining an approach for analyzing
the "new spaces and geographies" of digital phenomena and practices.

@leibowicz2016representing for energy There is no generally accepted
theory that explains diffusion rate heterogeneity across technologies,
but several factors are considered important. Greater unit scale and
larger market size contribute to slower diffusion. Requirements for
interrelated technologies or complex infrastructures also hinder the
diffusion process (Grubler, 2012).

Mobile phones benefited from early deployment in recreational boats and
automobiles, where the traditional competitor was not a viable option.
In the early stages of diffusion, performance is a more important driver
of adoption than cost competitiveness. Typically, significant cost
reductions only occur once the technology reaches a deployment level
capable of supporting standardization and mass production (Wilson,
2012).

Diffusion is a spatial (Hagerstrand, 1967) as well as a temporal
process, and historical evidence confirms that technologies diffuse at
different times, at different rates, and to different extents in
different places, and can be significantly influenced by policies
(Victor, 1993). An illustrative empirically based theory for technology
diffusion acrossmultiple regions is suggested by "Schmidt's Law"
(Grubler, 1990). With respect to a specific technology, it divides
regions into three groups: core, rim, and periphery. The core iswhere
the technology is invented, subject to experimentation, and first
deployed commercially. To develop the technology, the core must have
both sufficient innovative ability and economic motivation to make the
necessary resource commitment. As the technology spreads from the core
to the rim and eventually to the periphery, later adopters have the
advantage of benefiting from the experiences of earlier adopters via
knowledge spillover effects (Verdolini and Galeotti, 2011). At this
point, the technology has likely been refined and costs have likely
declined significantly. Schmidt's Law claims that, as a result,
diffusion proceeds at a faster rate in regions which adopt the
technology later. However, diffusion tends to be less pervasive in
regions where adoption is delayed, ultimately saturating at a lower
extent than in regions where adoption occurred earlier. This is often
attributed to a lack of proper institutions and infrastructures in later
adopters, markets whichmay not be as favorable to a technology, or the
availability of yet newer options that invite technological
leapfrogging.

Empirical evidence supports the validity of Schmidt's Law over a wide
range of technologies, time periods, and geographical contexts. A recent
meta-analysis of technology up-scaling found that diffusion accelerated
moving from the core to the rim and periphery for technologies as
diverse as natural gas power, oil refineries, and automobiles (Wilson,
2009). One historical example that conforms particularly well to
Schmidt's Law is the diffusion of coal power in Europe (Grubler, 2012).
England emerged as the core region for coal power because it had legal
and economic institutions that incentivized scientific pursuits,
domestic coal reserves, and a clear industrial motivation to replace
water power with coal. ...

Lastly, it can be globally optimal for innovative economies to deploy
advanced technologies more than what is locally optimal if this enables
faster diffusion in less advanced regions that could benefit from the
technology.

@wilson201281 Logistic growth describes an initial period of gradual
diffusion as a technology is introduced as a new commercial application,
moving then through a rapid, exponential growth phase, before slowing
and eventually saturating [@grubler1999dynamics]. The substitution of
incumbent technologies by new competitors leads to subsequent decline
and eventual obsolescence.

Early on in their lifecycle, new technologies are crude, imperfect, and
expensive (Rosenberg, 1994). New energy technologies are attractive for
their ability to perform a particular task or deliver a new or improved
energy service (Fouquet, 2010). This is often circumscribed by a
particular set of needs in a particular context: a market 'niche'.
End-users in niche markets are generally less sensitive to the effective
price of the energy service provided or have a higher willingness to pay
for its performance advantages (Fouquet, 2010). Thus initially,
performance dominates cost competitiveness (Wilson and Grubler, 2011).
Market niches afford some protection from competitive pressures,
allowing technologies to be tested and improved in applied settings,
reducing uncertainties with performance or market demand (Kemp et al.,
1998). Costs may only fall substantively after an extended period of
commercial experimentation, concurrent with the establishment of an
industrial base and characteristic moves towards standardisation and
mass production (Grubler, 1998). The influence of accumulating
production experience on costs is captured by the concept of learning.

@grubler1990rise Following the definition given by Rogers, 1983,
diffusion is the process by which an innovation is communicated through
certain communication channels over time among the members of a social
system. An innovation may be an idea, object or practice which is
perceived as new by an individual or another unit of adoption (e.g., an
organization) . Communication via communication channels refers to how
knowledge about an innovation is transferred between the members of a
social system. Communication takes time, and is therefore an important
aspect of innovation diffusion. In fact, all theoretical and empirical
diffusion studies agree that an innovation does not instantly diffuse
into a social system. Instead a typical time pattern of diffusion along
a S-shaped trajectory seems to be the rule. The S-shaped pattern of
diffusion appears to be a basic anthropologic phenomenon, as it is also
confirmed by a large number of studies· of primitive preindustrial
societies.

The scale of spatial innovation diffusion is similar\* to that of
temporal diffusion models: hierarchically decomposed.

>>>>

---
title: |
  Taylor & Francis Rmarkdown template for authors (\LaTeX\-based 
  \textsf{Interact} layout + Chicago author-date reference style)
type: ARTICLE TEMPLATE
author:
  - name: A. N. Author
    affil: a
    email: latex.helpdesk@tandf.co.uk
  - name: John Smith
    affil: b
    email: john.smith@uni-freiburg.de
  - name: Dominik Leutnant
    affil: c, \dagger, \ddagger
    email: leutnant@fh-muenster.de
affiliation:
  - num: a
    address: |
      Taylor & Francis, 4 Park Square, Milton Park, Abingdon, UK
  - num: b
    address: |
      Institut für Informatik, Albert-Ludwigs-Universität, Freiburg, Germany
  - num: c
    address: |
      Muenster University of Applied Sciences - 
      Institute for Infrastructure, Water, Resources, Environment,
      Correnstr. 25, 48149 Münster, Germany
thanks:
  author:
  - name: A. N. Author
    email: latex.helpdesk@tandf.co.uk
bibliography: interactcadsample.bib
appendix: appendix.tex
abstract: |
  This template is for authors who are preparing a manuscript for a Taylor & 
  Francis journal using the \LaTeX\ document preparation system and the 
  `interact} class file, which is available via selected journals' home 
  pages on the Taylor & Francis website.
keywords: |
  Sections; lists; figures; tables; mathematics; fonts; references; appendices
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
output: rticles::tf_article
---

# Introduction

In order to assist authors in the process of preparing a manuscript for a journal, the Taylor & Francis '\textsf{Interact}' layout style has been implemented as a \LaTeXe\ class file based on the `article` document class. A \textsc{Bib}\TeX\ bibliography style file and a sample bibliography are also provided in order to assist with the formatting of your references.

Commands that differ from or are provided in addition to standard \LaTeXe\ are described in this document, which is _not_ a substitute for a \LaTeXe\ tutorial.

The `interactcadsample.tex` file can be used as a template for a manuscript by cutting, pasting, inserting and deleting text as appropriate, using the preamble and the \LaTeX\ environments provided (e.g.\ `\begin{abstract}`, `\begin{keywords}`).

## The \textsf{Interact} class file

The `interact` class file preserves the standard \LaTeXe\ interface such that any document that can be produced using `article.cls` can also be produced with minimal alteration using the `interact` class file as described in this document.

If your article is accepted for publication it will be typeset as the journal requires in Minion Pro and/or Myriad Pro. Since most authors will not have these fonts installed, the page make-up is liable to alter slightly with the change of font. Also, the `interact` class file produces only single-column format, which is preferred for peer review and will be converted to two-column format by the typesetter if necessary during preparation of the proofs. Please therefore do not try to match the typeset format exactly, but use the standard \LaTeX\ fonts instead and ignore details such as slightly long lines of text or figures/tables not appearing in exact synchronization with their citations in the text: these details will be dealt with by the typesetter. Similarly, it is unnecessary to spend time addressing warnings in the log file -- if your .tex file compiles to produce a PDF document that correctly shows how you wish your paper to appear, such warnings will not prevent your source files being imported into the typesetter's program.

## Submission of manuscripts prepared using _\LaTeX_

Manuscripts for possible publication should be submitted to the Editors for review as directed in the journal's Instructions for Authors, and in accordance with any technical instructions provided in the journal's ScholarOne Manuscripts or Editorial Manager site. Your \LaTeX\ source file(s), the class file and any graphics files will be required in addition to the final PDF version when final, revised versions of accepted manuscripts are submitted.

Please ensure that any author-defined macros used in your article are gathered together in the preamble of your .tex file, i.e.\ before the `\begin{document}` command. Note that if serious problems are encountered in the coding of a document (missing author-defined macros, for example), the typesetter may resort to rekeying it.

# Using the `interact` class file

For convenience, simply copy the `interact.cls` file into the same directory as your manuscript files (you do not need to install it in your \TeX\ distribution). In order to use the `interact` document class, replace the command `\documentclass{article}` at the beginning of your document with the command `\documentclass{interact}`.

The following document-class options should _not_ be used with the `interact` class file:

* `10pt`, `11pt`, `12pt` -- unavailable;
* `oneside`, `twoside` -- not necessary, `oneside` is the default;
* `leqno`, `titlepage` -- should not be used;
* `twocolumn` -- should not be used;
* `onecolumn` -- not necessary as it is the default style.

To prepare a manuscript for a journal that is printed in A4 (two column) format, use the `largeformat` document-class option provided by `interact.cls`; otherwise the class file produces pages sized for B5 (single column) format by default. The `geometry` package should not be used to make any further adjustments to the page dimensions.

<!-- If your manuscript has supplementary content you can prepare this using the `suppldata` document-class option, which will suppress the `article history' date. This option must _not_ be used on any primary content. -->

# Additional features of the `interact` class file

## Title, authors' names and affiliations, abstracts and article types

## Abbreviations

A list of abbreviations may be included if required, enclosed within an `abbreviations` environment, i.e.\ `\begin{abbreviations}`\ldots`\end{abbreviations}`, immediately following the `abstract` environment.

## Keywords

A list of keywords may be included if required, enclosed within a `keywords` environment, i.e.\ `\begin{keywords}`\ldots`\end{keywords}`. Additional keywords in other languages (preceded by a translation of the word `keywords`) may also be included within the `keywords` environment if required.

## Subject classification codes

AMS, JEL or PACS classification codes may be included if required. The `interact` class file provides an `amscode` environment, i.e.\ `\begin{amscode}`\ldots`\end{amscode}`, a `jelcode` environment, i.e.\ `\begin{jelcode}`\ldots`\end{jelcode}`, and a `pacscode` environment, i.e.\ `\begin{pacscode}`\ldots`\end{pacscode}` to assist with this.

## Additional footnotes to the title or authors' names

<!-- The `\thanks` command may be used to create additional footnotes to the title or authors' names if required. Footnote symbols for this purpose should be used in the order -->
<!-- $^\ast$~(coded as `$^\ast$`), $\dagger$~(`$\dagger$`), $\ddagger$~(`$\ddagger$`), $\S$~(`$\S$`), $\P$~(`$\P$`), $\|$~(`$\|$`), -->
<!-- $\dagger\dagger$~(`$\dagger\dagger$`), $\ddagger\ddagger$~(`$\ddagger\ddagger$`), $\S\S$~(`$\S\S$`), $\P\P$~(`$\P\P$`). -->

Note that any `footnote`s to the main text will automatically be assigned the superscript symbols 1, 2, 3, etc. by the class file.^[If preferred, the `endnotes` package may be used to set the notes at the end of your text, before the bibliography. The symbols will be changed to match the style of the journal if necessary by the typesetter.]

# Embedding R code

## Code chunks

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE, out.width='80%'}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

# Some guidelines for using the standard features of \LaTeX

## Sections

The \textsf{Interact} layout style allows for five levels of section heading, all of which are provided in the `interact` class file using the standard \LaTeX\ commands `\section`, `\subsection`, `\subsubsection`, `\paragraph` and `\subparagraph`. Numbering will be automatically generated for all these headings by default.

## Lists

Numbered lists are produced using the `enumerate` environment, which will number each list item with arabic numerals by default. For example,

1. first item
2. second item
3. third item

Alternative numbering styles can be achieved by inserting an optional argument in square brackets to each `item`, e.g.\ `\item[(i)] first item`\, to create a list numbered with roman numerals at level one.

Bulleted lists are produced using the `itemize` environment. For example,

* First bulleted item
* Second bulleted item
* Third bulleted item

## Figures

```{r pressure-plot, fig.show='hide'}
plot(pressure)
```

The `interact` class file will deal with positioning your figures in the same way as standard \LaTeX. It should not normally be necessary to use the optional `[htb]` location specifiers of the `figure` environment in your manuscript; you may, however, find the `[p]` placement option or the `endfloat` package useful if a journal insists on the need to separate figures from the text.

Figure captions appear below the figures themselves, therefore the `\caption` command should appear after the body of the figure. For example, Figure~\ref{sample-figure} with caption and sub-captions is produced using the following commands:
```
\begin{figure}
\centering
\subfigure[An example of an individual figure sub-caption.]{%
\resizebox*{5cm}{!}{\includegraphics{path/to/fig}}}\hspace{5pt}
\subfigure[A slightly shorter sub-caption.]{%
\resizebox*{5cm}{!}{\includegraphics{path/to/fig}}}
\caption{Example of a two-part figure with individual sub-captions
 showing that captions are flush left and justified if greater
 than one line of text.} \label{sample-figure}
\end{figure}
```
\begin{figure}
\centering
\subfigure[An example of an individual figure sub-caption.]{%
\resizebox*{5cm}{!}{\includegraphics{`r knitr::fig_chunk('pressure-plot', 'pdf')`}}}\hspace{5pt}
\subfigure[A slightly shorter sub-caption.]{%
\resizebox*{5cm}{!}{\includegraphics{`r knitr::fig_chunk('pressure-plot', 'pdf')`}}}
\caption{Example of a two-part figure with individual sub-captions
 showing that captions are flush left and justified if greater
 than one line of text.} \label{sample-figure}
\end{figure}

To ensure that figures are correctly numbered automatically, the `\label` command should be included just after the `\caption` command, or in its argument.

The `\subfigure` command requires `subfigure.sty`, which is called in the preamble of the `interacttfssample.tex` file (to allow your choice of an alternative package if preferred) and included in the \textsf{Interact} \LaTeX\ bundle for convenience. Please supply any additional figure macros used with your article in the preamble of your .tex file.

The source files of any figures will be required when the final, revised version of a manuscript is submitted. Authors should ensure that these are suitable (in terms of lettering size, etc.) for the reductions they envisage.

The `epstopdf` package can be used to incorporate encapsulated PostScript (.eps) illustrations when using PDF\LaTeX, etc. Please provide the original .eps source files rather than the generated PDF images of those illustrations for production purposes.

## Tables
